Typed Functional Genetic Programming

### 2013-07-05 tex/thesis.tex
[tex]

\newcommand{\lam}[2]{( \lambda #1 . #2 )}

\begin{align*}
x   \in V \cup C          &\then x          \in \Lambda \\
M,N \in \Lambda           &\then (M~N)      \in \Lambda \\
x   \in V , M \in \Lambda &\then \lam{x}{M} \in \Lambda 
\end{align*}
\\
It is usual to use $V = \Sigma^+$ set of all non-empty finite strings of symbols 
from $\Sigma$ where $\Sigma$ is some alphabet set, e.g.  
$
\Sigma =
\setDots{a}{z} \cup 
\setDots{_0}{_9} $.

@@

We use upper case symbols such as 
$M,N,M_1,M_2,...,N_1,N_2,...$
to denote arbitrary lambda terms in contrast to
those in lower case such as
$a,b,c,...,x,y,z,$
$f_1,f_2,...,g_1,g_2,...$
denoting variable names, elements of $V$.\\

Examples of \lterms:\\

\begin{easylist}[itemize]
& $x$
& $\lam{x}{x}$
& $(\lam{x}{(x~x)}~\lam{x}{(x~x)})$
& $\lam{x}{\lam{y}{x}}$
& $\lam{f_1}{\lam{f_2}{\lam{x}{((f_1~x)~(f_2~x))}}}$
\end{easylist}~

@@

\begin{easylist}[itemize]
& $M_1~M_2~M_3~\dots~M_n$ for 
  $(\dots((M_1~M_2)~M_3)~\dots~M_n)$ 
& $\lam{x_1 x_2 \dots x_n }{M}$ for
  $\lam{x_1}{\lam{x_2}{\dots\lam{x_n}{M}\dots}}$
\end{easylist}~

@@

>>>>

\newcommand{\lamb}[2]{( \lambda #1 . #2 )}
\newcommand{\lam}[2]{\lambda #1 . #2}

\begin{align*}
x   \in V \cup C          &\then x           \in \Lambda \\
M,N \in \Lambda           &\then (M~N)       \in \Lambda 
\textit{~~~~~~(Function application)} \\
x   \in V , M \in \Lambda &\then \lamb{x}{M} \in \Lambda
\textit{~~~~~($\lambda$-abstraction)} 
\end{align*}
\\
It is usual to use $V = \Sigma^+$ set of all non-empty finite strings of symbols 
from $\Sigma$ where $\Sigma$ is some alphabet set, e.g.  
$
\Sigma =
\setDots{a}{z} \cup 
\setDots{_0}{_9} $.

@@

We use upper case symbols such as 
$M,N,M_1,M_2,...,N_1,N_2,...$
to denote arbitrary lambda terms in contrast to
those in lower case such as
$a,b,c,...,x,y,z,$
$f_1,f_2,...,g_1,g_2,...$
denoting variable names, elements of $V$.
Sometimes we will use lower case symbols
to denote arbitrary variable names (such as
$x$ in $\lamb{x}{M}$),
and at other times, we will use them
as specific variable names in specific terms 
(such as $x$ in $\lamb{x}{x}$).
The distinction between the two should be
clear from the context.\\

Examples of \lterms:

\begin{easylist}[itemize]
& $x$
& $\lamb{x}{x}$
& $(\lamb{x}{(x~x)}~\lamb{x}{(x~x)})$
& $\lamb{x}{\lamb{y}{x}}$
& $\lamb{f_1}{\lamb{f_2}{\lamb{x}{((f_1~x)~(f_2~x))}}}$
\end{easylist}~

@@

\begin{easylist}[itemize]
& $M_1~M_2~M_3~\dots~M_n$ for 
  $(\dots((M_1~M_2)~M_3)~\dots~M_n)$ 
& $\lam{x_1 x_2 \dots x_n }{M}$ for
  $\lamb{x_1}{\lamb{x_2}{\dots\lamb{x_n}{M}\dots}}$
\end{easylist}~

For example we can write
$\lamb{f_1}{\lamb{f_2}{\lamb{x}{((f_1~x)~(f_2~x))}}}$
as $\lam{f_1 f_2 x}{f_1~x~(f_2~x)}$.

\subsection{ Subterms, free variables and substitution }

Let us quickly define $ST(M)$ set of subterms of a term $M$:\\

\begin{easylist}[itemize]
& If $M = x$ then $ST(M) = {x}$.
& If $M = (P~Q)$ then $ST(M) = \{(P~Q)\} \cup ST(P) \cup ST(Q)$
& If $M = \lam{x}{M}$ then $ST(M) = \{\lam{x}{M}\} \cup ST(M)$
\end{easylist}~

\textbf{TODO FV a Substituci...}

@@

In order to perform computation there must be some
mechanism for term evaluation. In $\lambda$-calculus there
is $\beta$-reduction for this reason.\\

Any term of a form $\lamb{x}{M}N$ can be $\beta$-reduced to 
term $M[x:=N]$. This fact is written as relation of those
two terms in the following way:

$$\lamb{x}{M}N \rightarrow_\beta M[x:=N]$$
